\pkg{cubble}: An R Package for Organizing and Wrangling Multivariate Spatio-temporal Data

### 2022-06-16 jss/cubble-jss.tex
remove .aux and other knit associated files

\caption[A glyph map of the average maximum temperature by month for parts of Victoria and New South Wales weather stations in Australia for two five year periods (1971-1975, 2016-2020)]{A glyph map of the average maximum temperature by month for parts of Victoria and New South Wales weather stations in Australia for two five year periods (1971-1975, 2016-2020). An inset (top left) showing detail is the station Cobar (highlighted by black rectangle). The mothly trend is similar at all locations (low in the winter, high in the summer), and small increased temperatures, particularly in late summer can be seen at most stations.}\label{fig:basic-manip}
\end{figure}
\end{CodeChunk}

>>>>

\caption[A glyph map of the monthly maximum average temperature for weather stations in  Victoria and New South Wales for the periods (1971-1975, 2016-2020)]{A glyph map of the monthly maximum average temperature for weather stations in  Victoria and New South Wales for the periods (1971-1975, 2016-2020). The corresponding average time series for the Cobar station are display on the top left corner. From the glyph map we can observe that the monthly trend is similar for all locations (low in the winter, high in the summer), and small increased temperatures, particularly in late summer can be seen at most stations.}\label{fig:basic-manip}
\end{figure}
\end{CodeChunk}
